Matching Bullets

### 2015-12-17 imaging-paper.Rnw
ratio for cms

@
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{Densities of maximum CMS for Known Matches (KM) and Known Non Matches (KNM).}
<<cms-densities, echo=FALSE,  fig.width=7, fig.height=3.5, out.width='.7\\linewidth'>>=
ggplot(data=bstats) + 
    geom_density(aes(x=cms, fill=match), alpha=0.5) +
  xlab("maximum CMS") +
  scale_fill_brewer("", palette="Paired", labels=c("KNM", "KM")) +
  theme_bw() + 
  theme(legend.position=c(1,1), legend.justification=c(1,1),
        legend.background = element_rect(fill=alpha('white', 0.4))) 
@
\end{subfigure}
\caption{\label{fig:cms}Overview of the maximal number of consecutive maximal striae compared to matches.}
\end{figure}

@@

ggplot() +
  geom_polygon(aes(x=x, y=estimate, fill=match, colour=match), 
               data=densities, alpha=0.5) +
  xlab("Cross-correlation between cross sections") +
  scale_fill_brewer("", palette="Paired", labels=c("KNM", "KM")) +
  scale_colour_brewer("", palette="Paired", labels=c("KNM", "KM")) +
  theme_bw() + 
  ylab("Density estimate") +
  theme(legend.position=c(.975,1), legend.justification=c(1,1),
        legend.background = element_rect(fill=alpha('white', 0.4))) +
  geom_line(aes(x, pmin(5, kmtail/knmtail)), data=dframe) 
@
\end{subfigure}
\caption{A large cross-correlation between cross sections is indicative of matches between lands.}
\end{figure}

>>>>

@
\end{subfigure}
\begin{subfigure}[t]{\linewidth}
\caption{Densities of maximum CMS for Known Matches (KM) and Known Non Matches (KNM).}
<<cms-densities, echo=FALSE,  fig.width=7, fig.height=3.5, out.width='.7\\linewidth'>>=
x <- seq(0,29, by=0.03)
library(sm)
km <- sm.density(bstats$cms[bstats$match], display="none", eval.points=x)
knm <- sm.density(bstats$cms[!bstats$match], display="none", eval.points=x)
dframe <- data.frame(x = x, km=km$estimate, knm=knm$estimate)
dframe$kmtail <- rev(cumsum(rev(dframe$km)))/sum(dframe$km)
dframe$knmtail <- rev(cumsum(rev(dframe$knm)))/sum(dframe$knm)

densities <- data.frame(
  match = rep(c("KM", "KNM"), each=(length(x)+2)),
  x = rep(c(0, x, 29), times = 2),
  estimate = c(0, km$estimate, 0, 0, knm$estimate,0))

ggplot() +
  geom_polygon(aes(x=x, y=estimate, fill=match, group=match), colour="black",
               data=densities, alpha=0.5) +
xlab("maximum CMS") +
  scale_fill_brewer("", palette="Paired") +
  ylab("Density estimates") +
  theme_bw() + 
  theme(legend.position=c(1,1), legend.justification=c(1,1),
        legend.background = element_rect(fill=alpha('white', 0.4)))

ggplot(data=bstats) + 
    geom_density(aes(x=cms, fill=match), alpha=0.5) +
  xlab("maximum CMS") +
  scale_fill_brewer("", palette="Paired", labels=c("KNM", "KM")) +
  theme_bw() + 
  theme(legend.position=c(1,1), legend.justification=c(1,1),
        legend.background = element_rect(fill=alpha('white', 0.4))) 
@
\end{subfigure}
\caption{\label{fig:cms}Overview of the maximal number of consecutive maximal striae compared to matches.}
\end{figure}

@@

ggplot() +
  geom_polygon(aes(x=x, y=estimate, fill=match), colour="black",
               data=densities, alpha=0.5) +
  xlab("Cross-correlation between cross sections") +
  scale_fill_brewer("", palette="Paired", labels=c("KNM", "KM")) +
#  scale_colour_brewer("", palette="Paired", labels=c("KNM", "KM")) +
  theme_bw() + 
  ylab("Density estimate") +
  theme(legend.position=c(.975,1), legend.justification=c(1,1),
        legend.background = element_rect(fill=alpha('white', 0.4))) +
  geom_line(aes(x, pmin(5, kmtail/knmtail)), data=dframe) 
@
\end{subfigure}
\caption{A large cross-correlation between cross sections is indicative of matches between lands.}
\end{figure}
